Assignment 2

### 2025-03-12 code/Reddit_API.qmd
added keyword search & subreddit columns to reddit_comments.xlsx
adding eda code

library(tidyverse)
library(readxl)
library(writexl)
# install.packages("devtools")
# devtools::install_github('ivan-rivera/RedditExtractor')
library(RedditExtractoR)
```

@@

    -   The effects of remove work policies.

@@

```{r}
reddit_unclean <- readRDS("D:/repos/SURV622_Assignment/data/posts_data.RDS")
glimpse(reddit_unclean)
```

@@

>>>>

library(tidyverse)
library(writexl)
# install.packages("devtools")
# devtools::install_github('ivan-rivera/RedditExtractor')
library(RedditExtractoR)
```

@@

    -   The effects of remote work policies.

@@

```{r}
reddit_unclean <- readRDS("~/repos/SURV622_Assignment/data/posts_data.RDS")
glimpse(reddit_unclean)
```

@@

The comments are still missing subreddit and keyword search information. We will join this information from the reddit_clean data.

```{r}
reddit_comments <- reddit_comments |> 
  left_join(
    # select needed variables
    reddit_clean |> 
      select(url, subreddit, search_term),
    relationship = "many-to-many"
  )

glimpse(reddit_comments)
```
